---
title: "Basic Measurement Reactivity Sim"
format: html
editor: visual
---

## Model Setup


Let's imagine we have the following model for a treatment we want to estimate for a pretest posttest design

$$y_2 = \beta_0 + \beta_1 treatment + \beta_2 y_1$$

If we have measurement reactivity, the problem is that the act of taking the measurement at time 1 ($y_1$) acts as confounder, meaning we can't know if $\beta_1$ might look different if $y_1$ were not measured.

A standard solution might be to omite the pretest and just do a between subjects comparison without any pretest as a covariate

$$y_2 = \beta_0 + \beta_1 treatment$$

One issue with this approach is it is possible that baseline scores interact with the treatment, and that becomes impossible to to measure

$$y_2 = \beta_0 + \beta_1 treatment + \beta_2 y_1 + \beta_3 (treatment) (y_1)$$

Our approach uses a planned missingness design, where participants are randomized into a design where $y_1$ measurements are either observed or missing, and Type B auxiliary variables are used to impute the missing values, eliminating the effect of measurement reactivity.

I sketched out a simple simulation with the following data generating model

- $y_1$ is pretest measurement
- $y_2$ is posttest measurement
- $t_t$ is the target treatment
- $t_m$ is the treatment effect of measurement reactivity
- $t_{m,t}$ is a compensatory effect of measurement reactivity (how much measurement reactivity offsets the treatment effect)
- $R^2_{aux}$ is the proportion of variance in $y_1$ explained by auxiliary variables
- $K$ is the number of auxiliary variables
- $N$ is the total sample size
- $n_m$ is the sample size where $y_i$ is measured
- $treatment$ is the treatment condition (0 or 1)
- $measure$ is the measurement condition (0 or 1)
- $mod_y$ is the moderation effect of $y_1$ on $treatment$

The data generating process is based on

$$\boldsymbol{aux} \sim MVN(\boldsymbol{0}, \boldsymbol{I})$$

$$y_{1,i} = \sum aux_i + \epsilon_{impute,i}$$

where $\sigma_{epsilon_{impute}} = K\frac{1-R^2_{aux}}{R^2_{aux}}$

$$y_{2,i} = y_{1,i} + t_t (treatment_i) + t_m (measure_i) + mod_y (y_{1,i}) (treatment_i) + t_{m,t} (treatment) (measure)$$

In the first version of the simple simulation I set 


- $t_t = .3$
- $t_m = .2$
- $t_{m,t} = .75 (t_m)$, meaning that 75% of the effect of measurement "overlapped" with the treatment effect
- $R^2_{aux} = .33$
- $N = 400$
- $n_m = .4 (N)$
- $K = 3$


```{r}
library(MASS)
library(tidyverse)
library(effectsize)
library(mice)
library(mitml)

## Set parameters
n <- 400 ## Sample Size
r2 <- .33 ## R2 of missing variable on Type B aux variables
k <- 3 ## number of aux variables
cor_mat <- diag(1, k, k) ## Correlations for aux variables (independent for now)  
t_i <- .3 ## treatment of interest
p_m <- .4 ## proportion in measured condition
n_m <- round(n * p_m) ## N in measured condition
n_no_m <- n - n_m ## N in unmeasured condition
m <- c(rep(1, n_m), rep(0, n_no_m)) ## dummy variable for measurement
cond <- rep(c(0,1), n/2)
t_m <- .2 ## treatment effect of measurement
t_int <- -.75 * t_m


n_imps <- 10 ## set number of imputations

iter <- 200
res_df <- data.frame(between_res = rep(NA, iter),
                    within_res = rep(NA, iter),
                     mi_res = rep(NA, iter))



for(i in 1:iter){

predictor_matrix <- mvrnorm(n, rep(0, k), cor_mat) ## Create predictor matrix
resid <- sqrt(k * (1 - r2)/r2) ## Define residual of y



y1 <- rnorm(n, rowSums(predictor_matrix), resid) ## Define y as linear combo of predictors and error
sd_y <- sqrt((k + resid^2)) ## sd of y


y1_s <- y1/sd_y ## standardize y1



y2 <- y1_s + rnorm(n, t_i * cond + t_m * m + t_int * cond * m) ## define y2 as combo of predictors
y2_between <- y1_s + rnorm(n, t_i * cond) ## y2 for fully between subjects design
y2_within <- y1_s + rnorm(n, t_i * cond + t_m * m + t_int * cond) ## y2 for fully between subjects design


df <- data.frame(y1 = y1_s, y2 = y2, y2_between = y2_between, y2_within = y2_within,
                 m = m, cond = cond)


lm_between <- lm(y2_between ~ cond, df) ## model for no pretest
lm_within <- lm(y2_within ~ cond + y1, df) ## model where all get pretest

res_df$between_res[i] <- lm_between$coefficients[2]
res_df$within_res[i] <- lm_within$coefficients[2]


df_impute <- df %>% mutate(y1 = ifelse(m == 0, NA, y1)) ## set planned missingness

df_mice <- cbind(df_impute %>% select(y1), predictor_matrix) ## combine y1 with aux vars



mimps <- mice(df_mice, m = n_imps, printFlag = FALSE) ## mice imputation

pmm_imps <- complete(mimps, action = "long") %>%
   mutate(y2 = rep(df_impute$y2, n_imps),
           cond = rep(df_impute$cond, n_imps),
           m = rep(df_impute$m, n_imps)) ## add variables to imputed dataset

pmm_imps_list <- as.mitml.list(split(pmm_imps, pmm_imps$.imp)) ## split datasets


analysis_pmm <- with(pmm_imps_list, lm(y2 ~ y1 + cond + m + cond * m)) ## imputed model

lm_impute <- testEstimates(analysis_pmm)

res_df$mi_res[i] <- as.data.frame(lm_impute$estimates)$Estimate[3]




}


res_df <- res_df %>%
  mutate(between = between_res - t_i,
         within = within_res - t_i,
         mi = mi_res - t_i)


res_df_long <- res_df %>% select(between, within, mi) %>% pivot_longer(1:3, names_to = "model", values_to = "bias")

res_df_long %>% group_by(model) %>%
  summarize(mean_bias = mean(bias),
         rmse = sqrt(mean(bias^2)))


ggplot(res_df_long, aes(x = model, y = bias)) + geom_violin() + geom_jitter()

```


The planned missingness (mi) condition and between subjects condition perform similarly here. The main advantage of the planned missingness condition is don't need to administer a pretest to all of the participants.

However, now let's consider a moderation effect of $y_1$ and set $mod_y = -.1$, meaning the effect of the treatment is reduced for people who start out with higher baseline scores. In the fully between subjects condition, it is impossible to estimate this moderation effect. We can only do so with some measurement or estimate of $y_1$

```{r}


y_mod <- -.1


res_df_int <- data.frame(between_res = rep(NA, iter),
                     within_res = rep(NA, iter),
                     mi_res = rep(NA, iter),
                     within_res_int = rep(NA, iter),
                     mi_res_int = rep(NA, iter))





for(i in 1:iter){
  
  predictor_matrix <- mvrnorm(n, rep(0, k), cor_mat) ## Create predictor matrix
  resid <- sqrt(k * (1 - r2)/r2) ## Define residual of y
  
  
  
  y1 <- rnorm(n, rowSums(predictor_matrix), resid) ## Define y as linear combo of predictors and error
  sd_y <- sqrt((k + resid^2)) ## sd of y
  
  
  y1_s <- y1/sd_y ## standardize y1
  
  
  
  y2 <-  rnorm(n, y1_s + t_i * cond + y_mod * cond * y1_s  + t_m * m + t_int * cond * m) ## define y2 as combo of predictors
  y2_between <- y1_s + rnorm(n, t_i * cond) ## y2 for fully between subjects design
  y2_within <- y1_s + rnorm(n, t_i * cond + t_m * m + t_int * cond) ## y2 for fully between subjects design
  
  
  df <- data.frame(y1 = y1_s, y2 = y2, y2_between = y2_between, y2_within = y2_within,
                   m = m, cond = cond)
  
  
  lm_between <- lm(y2_between ~ cond, df) ## model for no pretest
  lm_within <- lm(y2_within ~ cond + y1 + y1 * cond, df) ## model where all get pretest
  
  res_df_int$between_res[i] <- lm_between$coefficients[2]
  res_df_int$within_res[i] <- lm_within$coefficients[2]
  res_df_int$within_res_int[i] <- lm_within$coefficients[4]
  
  
  df_impute <- df %>% mutate(y1 = ifelse(m == 0, NA, y1)) ## set planned missingness
  
  df_mice <- cbind(df_impute %>% select(y1), predictor_matrix) ## combine y1 with aux vars
  
  
  
  mimps <- mice(df_mice, m = n_imps, printFlag = FALSE) ## mice imputation
  
  pmm_imps <- complete(mimps, action = "long") %>%
    mutate(y2 = rep(df_impute$y2, n_imps),
           cond = rep(df_impute$cond, n_imps),
           m = rep(df_impute$m, n_imps)) ## add variables to imputed dataset
  
  pmm_imps_list <- as.mitml.list(split(pmm_imps, pmm_imps$.imp)) ## split datasets
  
  
  analysis_pmm <- with(pmm_imps_list, lm(y2 ~ y1 + cond + y1 * cond + m + cond * m)) ## imputed model
  
  lm_impute <- testEstimates(analysis_pmm)
  
  res_df_int$mi_res[i] <- as.data.frame(lm_impute$estimates)$Estimate[3]
  res_df_int$mi_res_int[i] <- as.data.frame(lm_impute$estimates)$Estimate[5]
  
  
  
  
}


res_df_int <- res_df %>%
  mutate(between = between_res - t_i,
         within = within_res - t_i,
         mi = mi_res - t_i,
         within_int = within_res - t_i,
         mi_int = mi_res - t_i)

## main effects
res_df_long <- res_df_int %>% select(between, within, mi) %>% pivot_longer(1:3, names_to = "model", values_to = "bias")

res_df_long %>% group_by(model) %>%
  summarize(mean_bias = mean(bias),
            rmse = sqrt(mean(bias^2)))


ggplot(res_df_long, aes(x = model, y = bias)) + geom_violin() + geom_jitter()

## interactions effects
res_df_long_int <- res_df_int %>% select(within_int, mi_int) %>% pivot_longer(1:2, names_to = "model", values_to = "bias")

res_df_long_int %>% group_by(model) %>%
  summarize(mean_bias = mean(bias),
            rmse = sqrt(mean(bias^2)))


ggplot(res_df_long_int, aes(x = model, y = bias)) + geom_violin() + geom_jitter()
```


Our approach produces unbiased estimates of the moderation effect, while the version that has complete pretest measurement has severe bias. 
