---
title: "Basic Measurement Reactivity Sim"
format:
  html:
    embed-resources: true
editor: visual
editor_options: 
  chunk_output_type: console
---

## Model Setup

Let's imagine we have the following model for a treatment we want to estimate for a prettest posttest design

$$y_2 = \beta_0 + \beta_1 treatment + \beta_2 y_1$$

If we have measurement reactivity, the problem is that the act of taking the measurement at time 1 ($y_1$) acts as confounder, meaning we can't know if $\beta_1$ might look different if $y_1$ were not measured.

A standard solution might be to omit the prettest and just do a between subjects comparison without any prettest as a covariate

$$y_2 = \beta_0 + \beta_1 treatment$$

One issue with this approach is it is possible that baseline scores interact with the treatment, and that becomes impossible to to measure

$$y_2 = \beta_0 + \beta_1 treatment + \beta_2 y_1 + \beta_3 (treatment) (y_1)$$

Our approach uses a planned missingness design, where participants are randomized into a design where $y_1$ measurements are either observed or missing, and Type B auxiliary variables are used to impute the missing values, eliminating the effect of measurement reactivity.

I sketched out a simple simulation with the following data generating model

-   $K$ is the number of auxiliary variables
-   $N$ is the total sample size
-   $treatment$ is the treatment condition (0 or 1)
-   $prettest$ is the measurement condition (0 or 1)
-   $y_1$ is prettest measurement
-   $y_2$ is posttest measurement
-   $n_{pre}$ is the sample size in the prettest condition
-   $\beta_1$ is the effect of the treatment (compared to control) when there is no pretest at the average baseline score ($y_1$)
-   $\beta_2$ is the effect of the prettest being elicited on the posttest in the control condition (no target treatment) at the average baseline score ($y_1$)
-   $\beta_3$ is the effect of the prettest score on posttest (set to 1 for simplicity) in the control condition when there is no prettest
-   $\beta_4$ is the difference in treatment effect (change in $\beta_1$) when the prettest is taken (vs when it is not) at the average baseline score ($y_1$)
-   $\beta_5$ is the change in the effect of the treatment ($\beta_1$) for one unit increase in baseline score ($y_1$) when the prettest is not taken.
-   $\beta_6$ is the change in the effect of the prettest ($\beta_2$) for one unit increase in baseline score ($y_1$) when the in the control condition
-   $\beta_7$ is the change in the change the effect of treatment for one unit increase in baseline score ($\beta_5$) when the prettest is taken
-   $R^2_{aux}$ is the proportion of variance in $y_1$ explained by auxiliary variables

The data generating process is based on

$$\boldsymbol{aux} \sim MVN(\boldsymbol{0}, \boldsymbol{I})$$ **NOTE:** for now this implies predictors are independent. We should manipulate this!

$$y_{1,i} = \sum aux_i + \epsilon_{impute,i}$$

where $\sigma_{\epsilon_{impute,i}} = K\frac{1-R^2_{aux}}{R^2_{aux}}$

$y_{2,i} = \beta_0 + \beta_1 treatment_i +  \beta_2(prettest_i)  + \beta_3 (y_{1,i}) +  \beta_4(treatment_i)(prettest_i) + \beta_5 (treatment_i) (y_{1,i}) + \beta_6 (prettest_i) (y_{1,i}) + \beta_7 (treatment_i) (prettest_i) (y_{1,i}) +\epsilon_{y2}$

In the first version of the simple simulation I set

-   $\beta_0 = 0$ mean of $y_2$ in control + no prettest condition (set to 0 for simplicity)
-   $\beta_1 = .3$ (should be manipulated)
-   $\beta_2 = .2$ (should be manipulated)
-   $\beta_3 = 1$ (does not need to be manipulated)
-   $\beta_4 = - .75 (\beta_1)$, meaning that 75% of the effect of measurement "overlapped" with the treatment effect (should be manipulated and we should think about if this is the right way to do)
-   $\beta_5 = - .1$ (should be manipulated)
-   $\beta_6 = 0$ (should be manipulated)
-   $\beta_7 = 0$ (should be manipulated)
-   $\sigma_{\epsilon_{y2}} = 1$ (for simplicity, does not need to be manipulated I don't think)
-   $R^2_{aux} = .33$ (should be manipulated)
-   $N = 400$ (should be manipulated)
-   $n_pre = .4 (N)$ (maybe manipulated?)
-   $K = 3$ (maybe manipulated?)

```{r message = FALSE, warning = FALSE}
library(MASS)
library(effectsize)
library(mice)
library(mitml)
library(brms)
library(rstan)
library(mdmb)
library(tidyverse)
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)



## Set parameters
n <- 400 ## Sample Size
r2_aux <- .33 ## R2 of missing variable on Type B aux variables
K <- 3 ## number of aux variables
cor_mat <- diag(1, K, K) ## Correlations for aux variables (independent for now)  

p_pre <- .4 ## proportion in measured condition
n_pre <- round(n * p_pre) ## N in measured condition
n_no_pre <- n - n_pre ## N in unmeasured condition
prettest <- c(rep(1, n_pre), rep(0, n_no_pre)) ## dummy variable for measurement
treatment <- rep(c(0,1), n/2)
beta1 <- .3 ## treatment of interest
beta2 <- .2 ## treatment effect of measurement
beta3 <- 1
beta4 <-  -.75 * beta1
beta5 <- -.1
beta6 <- 0
beta7 <- 0
sigma <- 1
set.seed(1204021) # for reproducibility

## true values in DF (we will need to figure out how to handle this
## when we manipulate)
par_df <- data.frame(parameter = c(paste0("beta", 0:7), "sigma"),
                     definition = c("intercept","treatment", "prettested",
                                    "baseline (y1)", "treatment * prettested",
                                    "treatment * y1","prettested * y1", 
                                    "treatement * prettested * y1","residual"),
                     true_value = c(0, beta1, beta2, beta3, beta4, beta5, 
                                    beta6, beta7, sigma))


n_imps <- 100 ## set number of imputations for mice

iter <- 100

## What else should we add here?
## Freq. test stats information? p, t, se, CI
## Bayesian credible intervals? What other bayes stuff?
if (file.exists("simple sim results.RDS")) {
  point_df <- readRDS("simple sim results.RDS")
} else {


make_df <- function(iter) {
  data.frame(
    # beta0
    between_beta0 = rep(NA, iter),
    full_pretest_beta0 = rep(NA, iter),
    true_beta0 = rep(NA, iter),
    fiml_beta0 = rep(NA, iter),
    mi_beta0 = rep(NA, iter),
    brm_beta0 = rep(NA, iter),
    
    # beta1
    between_beta1 = rep(NA, iter),
    full_pretest_beta1 = rep(NA, iter),
    true_beta1 = rep(NA, iter),
    fiml_beta1 = rep(NA, iter),
    mi_beta1 = rep(NA, iter),
    brm_beta1 = rep(NA, iter),
    
    # beta2
    between_beta2 = rep(NA, iter),
    full_pretest_beta2 = rep(NA, iter),
    true_beta2 = rep(NA, iter),
    fiml_beta2 = rep(NA, iter),
    mi_beta2 = rep(NA, iter),
    brm_beta2 = rep(NA, iter),
    
    # beta3
    between_beta3 = rep(NA, iter),
    full_pretest_beta3 = rep(NA, iter),
    true_beta3 = rep(NA, iter),
    fiml_beta3 = rep(NA, iter),
    mi_beta3 = rep(NA, iter),
    brm_beta3 = rep(NA, iter),
    
    # beta4
    between_beta4 = rep(NA, iter),
    full_pretest_beta4 = rep(NA, iter),
    true_beta4 = rep(NA, iter),
    fiml_beta4 = rep(NA, iter),
    mi_beta4 = rep(NA, iter),
    brm_beta4 = rep(NA, iter),
    
    # beta5
    between_beta5 = rep(NA, iter),
    full_pretest_beta5 = rep(NA, iter),
    true_beta5 = rep(NA, iter),
    fiml_beta5 = rep(NA, iter),
    mi_beta5 = rep(NA, iter),
    brm_beta5 = rep(NA, iter),
    
    # beta6
    between_beta6 = rep(NA, iter),
    full_pretest_beta6 = rep(NA, iter),
    true_beta6 = rep(NA, iter),
    fiml_beta6 = rep(NA, iter),
    mi_beta6 = rep(NA, iter),
    brm_beta6 = rep(NA, iter),
    
    # beta7
    between_beta7 = rep(NA, iter),
    full_pretest_beta7 = rep(NA, iter),
    true_beta7 = rep(NA, iter),
    fiml_beta7 = rep(NA, iter),
    mi_beta7 = rep(NA, iter),
    brm_beta7 = rep(NA, iter),
    
    # sigma
    between_sigma = rep(NA, iter),
    full_pretest_sigma = rep(NA, iter),
    true_sigma = rep(NA, iter),
    fiml_sigma = rep(NA, iter),
    mi_sigma = rep(NA, iter),
    brm_sigma = rep(NA, iter)
  )
}

point_df <- make_df(iter)
lci_df   <- make_df(iter)
uci_df   <- make_df(iter)

t1 <- Sys.time() # save start time


for(i in 1:iter){
## Create auxiliary variable matrix 
aux_matrix <- mvrnorm(n, rep(0, K), cor_mat) ## Create predictor matrix
resid <- sqrt(K * (1 - r2_aux)/r2_aux) ## Define residual of y
aux_matrix <- as.data.frame(aux_matrix)
names(aux_matrix) <- paste0("x", 1:ncol(aux_matrix))


y1 <- rnorm(n, rowSums(aux_matrix), resid) ## Define y as linear combo of predictors and error
sd_y <- sqrt((K + resid^2)) ## sd of y


y1_s <- y1/sd_y ## standardize y1 (for simplicity? idk)



y2 <- rnorm(n, beta1 * treatment + 
              beta2 * prettest + beta3 * y1_s + 
              beta4 * treatment * prettest + 
              beta5 * treatment * y1_s + 
              beta6 * prettest * y1_s + 
              beta7 * treatment * prettest * y1_s) ## define y2 as specified data generating process

y2_between <- rnorm(n, beta1 * treatment + 
              beta2 * 0 + beta3 * y1_s + 
              beta4 * treatment * 0 + 
              beta5 * treatment * y1_s + 
              beta6 * 0 * y1_s + 
              beta7 * treatment * 0 * y1_s) ## y2 for fully between subjects design

y2_pretest <-  rnorm(n, beta1 * treatment + 
              beta2 * 1 + beta3 * y1_s + 
              beta4 * treatment * 1 + 
              beta5 * treatment * y1_s + 
              beta6 * 1 * y1_s + 
              beta7 * treatment * 1 * y1_s)

df <- data.frame(y1 = y1_s, y2 = y2, y2_between = y2_between,
                 y2_pretest = y2_pretest,
                 prettest = prettest, treatment = treatment)


lm_between <- lm(y2_between ~ treatment, df) ## model for no prettest
lm_pretest <- lm(y2_pretest ~ treatment * y1, df) ## model where all get prettest but measurement reactivity isn't (can't be) addressed

lm_true <- lm(y2 ~ treatment * prettest * y1, df) ## Theoretically correct model (if we could effects of measurement reactivity)

## Extract Results from "traditional" models



point_df$between_beta0[i] <- lm_between$coefficients[1]
point_df$between_beta1[i] <- lm_between$coefficients[2]
point_df$between_sigma[i] <- sigma(lm_between)

lci_df$between_beta0[i] <- confint(lm_between)[1,1]
lci_df$between_beta1[i] <- confint(lm_between)[2,1]

uci_df$between_beta0[i] <- confint(lm_between)[1,2]
uci_df$between_beta1[i] <- confint(lm_between)[2,2]

point_df$full_pretest_beta0[i] <- lm_pretest$coefficients[1]
point_df$full_pretest_beta1[i] <- lm_pretest$coefficients[2]
point_df$full_pretest_beta3[i] <- lm_pretest$coefficients[3]
point_df$full_pretest_beta4[i] <- lm_pretest$coefficients[4]
point_df$full_pretest_sigma[i] <- sigma(lm_pretest)



lci_df$full_pretest_beta0[i] <- confint(lm_pretest)[1,1]
lci_df$full_pretest_beta1[i] <- confint(lm_pretest)[2,1]
lci_df$full_pretest_beta3[i] <- confint(lm_pretest)[3,1]
lci_df$full_pretest_beta4[i] <- confint(lm_pretest)[4,1]

uci_df$full_pretest_beta0[i] <- confint(lm_pretest)[1,2]
uci_df$full_pretest_beta1[i] <- confint(lm_pretest)[2,2]
uci_df$full_pretest_beta3[i] <- confint(lm_pretest)[3,2]
uci_df$full_pretest_beta4[i] <- confint(lm_pretest)[4,2]



## Extract parameters from "true" theoretically correct model




point_df$true_beta0[i] <- lm_true$coefficients[1]
point_df$true_beta1[i] <- lm_true$coefficients[2]
point_df$true_beta2[i] <- lm_true$coefficients[3]
point_df$true_beta3[i] <- lm_true$coefficients[4]
point_df$true_beta4[i] <- lm_true$coefficients[5]
point_df$true_beta5[i] <- lm_true$coefficients[6]
point_df$true_beta6[i] <- lm_true$coefficients[7]
point_df$true_beta7[i] <- lm_true$coefficients[8]
point_df$true_sigma[i] <- sigma(lm_true)



lci_df$true_beta0[i] <-confint(lm_true)[1,1]
lci_df$true_beta1[i] <-confint(lm_true)[2,1]
lci_df$true_beta2[i] <-confint(lm_true)[3,1]
lci_df$true_beta3[i] <-confint(lm_true)[4,1]
lci_df$true_beta4[i] <-confint(lm_true)[5,1]
lci_df$true_beta5[i] <-confint(lm_true)[6,1]
lci_df$true_beta6[i] <-confint(lm_true)[7,1]
lci_df$true_beta7[i] <-confint(lm_true)[8,1]

uci_df$true_beta0[i] <-confint(lm_true)[1,2]
uci_df$true_beta1[i] <-confint(lm_true)[2,2]
uci_df$true_beta2[i] <-confint(lm_true)[3,2]
uci_df$true_beta3[i] <-confint(lm_true)[4,2]
uci_df$true_beta4[i] <-confint(lm_true)[5,2]
uci_df$true_beta5[i] <-confint(lm_true)[6,2]
uci_df$true_beta6[i] <-confint(lm_true)[7,2]
uci_df$true_beta7[i] <-confint(lm_true)[8,2]


## Set missing data data
df_impute <- df %>% mutate(y1 = ifelse(prettest ==  0, NA, y1)) ## set planned missingness

## dataset for model-based maximum likelihood and brms imputation (has other variables)

df_ml_brm <- cbind(df_impute, aux_matrix) ## combine y1 with aux vars


## Maximum Likelihood

intg.nods <- seq(min(df_ml_brm$y1[!is.na(df_ml_brm$y1)]), max(df_ml_brm$y1[!is.na(df_ml_brm$y1)]), length.out = 30) ## set integration nodes


## factorized models
model.s1 <- list("model" = "linreg", "formula" = x1 ~ x2 + x3 + y2 + y1)
model.s2 <- list("model" = "linreg", "formula" = x2 ~ x3 + y2 + y1)
model.s3 <- list("model" = "linreg", "formula" = x3 ~ y2 + y1)
model.s4 <- list("model" = "linreg", "formula" = y2 ~ treatment * prettest * y1)
model.s5 <- list("model" = "linreg", "formula" = y1 ~ 1, 
                 nodes = intg.nods)

## separate "extra" models
extra.mods <- list(model.s1 = model.s1,
                   model.s2 = model.s2,
                   model.s3 = model.s3,
                   model.s5 = model.s5)


## estimation
ml_result <- frm_em(dat = df_ml_brm, dep = model.s4, 
              ind = extra.mods)



point_df$fiml_beta0[i] <- ml_result$partable$est[1]
point_df$fiml_beta1[i] <- ml_result$partable$est[2]
point_df$fiml_beta2[i] <- ml_result$partable$est[3]
point_df$fiml_beta3[i] <- ml_result$partable$est[4]
point_df$fiml_beta4[i] <- ml_result$partable$est[5]
point_df$fiml_beta5[i] <- ml_result$partable$est[6]
point_df$fiml_beta6[i] <- ml_result$partable$est[7]
point_df$fiml_beta7[i] <- ml_result$partable$est[8]
point_df$fiml_sigma[i] <- ml_result$partable$est[9]


lci_df$fiml_beta0[i] <- ml_result$partable$lower95[1]
lci_df$fiml_beta1[i] <- ml_result$partable$lower95[2]
lci_df$fiml_beta2[i] <- ml_result$partable$lower95[3]
lci_df$fiml_beta3[i] <- ml_result$partable$lower95[4]
lci_df$fiml_beta4[i] <- ml_result$partable$lower95[5]
lci_df$fiml_beta5[i] <- ml_result$partable$lower95[6]
lci_df$fiml_beta6[i] <- ml_result$partable$lower95[7]
lci_df$fiml_beta7[i] <- ml_result$partable$lower95[8]
lci_df$fiml_sigma[i] <- ml_result$partable$lower95[9]

uci_df$fiml_beta0[i] <- ml_result$partable$upper95[1]
uci_df$fiml_beta1[i] <- ml_result$partable$upper95[2]
uci_df$fiml_beta2[i] <- ml_result$partable$upper95[3]
uci_df$fiml_beta3[i] <- ml_result$partable$upper95[4]
uci_df$fiml_beta4[i] <- ml_result$partable$upper95[5]
uci_df$fiml_beta5[i] <- ml_result$partable$upper95[6]
uci_df$fiml_beta6[i] <- ml_result$partable$upper95[7]
uci_df$fiml_beta7[i] <- ml_result$partable$upper95[8]
uci_df$fiml_sigma[i] <- ml_result$partable$upper95[9]




## dataset for agnostic mice imputation (ignoring other variables)

df_mice <- cbind(df_impute %>% select(y1), aux_matrix) ## combine y1 with aux vars


## Multiple imputation
mimps <- mice(df_mice, m = n_imps, printFlag = FALSE) ## mice imputation

pmm_imps <- complete(mimps, action = "long") %>%
   mutate(y2 = rep(df_impute$y2, n_imps),
           treatment = rep(df_impute$treatment, n_imps),
           prettest = rep(df_impute$m, n_imps)) ## add variables to imputed dataset


pmm_imps_list <- as.mitml.list(split(pmm_imps, pmm_imps$.imp)) ## split datasets


analysis_pmm <- with(pmm_imps_list, lm(y2 ~ treatment * prettest * y1)) ## imputed model

lm_impute <- testEstimates(analysis_pmm, extra.pars = TRUE)


point_df$mi_beta0[i] <- as.data.frame(lm_impute$estimates)$Estimate[1]
point_df$mi_beta1[i] <- as.data.frame(lm_impute$estimates)$Estimate[2]
point_df$mi_beta2[i] <- as.data.frame(lm_impute$estimates)$Estimate[3]
point_df$mi_beta3[i] <- as.data.frame(lm_impute$estimates)$Estimate[4]
point_df$mi_beta4[i] <- as.data.frame(lm_impute$estimates)$Estimate[5]
point_df$mi_beta5[i] <- as.data.frame(lm_impute$estimates)$Estimate[6]
point_df$mi_beta6[i] <- as.data.frame(lm_impute$estimates)$Estimate[7]
point_df$mi_beta7[i] <- as.data.frame(lm_impute$estimates)$Estimate[8]
point_df$mi_beta7[i] <- as.data.frame(lm_impute$estimates)$Estimate[8]
point_df$mi_sigma[i] <- sqrt(lm_impute$extra.pars)


lci_df$mi_beta0[i] <-as.data.frame(confint(lm_impute))$`2.5 %`[1]
lci_df$mi_beta1[i] <-as.data.frame(confint(lm_impute))$`2.5 %`[2]
lci_df$mi_beta2[i] <-as.data.frame(confint(lm_impute))$`2.5 %`[3]
lci_df$mi_beta3[i] <-as.data.frame(confint(lm_impute))$`2.5 %`[4]
lci_df$mi_beta4[i] <-as.data.frame(confint(lm_impute))$`2.5 %`[5]
lci_df$mi_beta5[i] <-as.data.frame(confint(lm_impute))$`2.5 %`[6]
lci_df$mi_beta6[i] <-as.data.frame(confint(lm_impute))$`2.5 %`[7]
lci_df$mi_beta7[i] <-as.data.frame(confint(lm_impute))$`2.5 %`[8]

uci_df$mi_beta0[i] <-as.data.frame(confint(lm_impute))$`97.5 %`[1]
uci_df$mi_beta1[i] <-as.data.frame(confint(lm_impute))$`97.5 %`[2]
uci_df$mi_beta2[i] <-as.data.frame(confint(lm_impute))$`97.5 %`[3]
uci_df$mi_beta3[i] <-as.data.frame(confint(lm_impute))$`97.5 %`[4]
uci_df$mi_beta4[i] <-as.data.frame(confint(lm_impute))$`97.5 %`[5]
uci_df$mi_beta5[i] <-as.data.frame(confint(lm_impute))$`97.5 %`[6]
uci_df$mi_beta6[i] <-as.data.frame(confint(lm_impute))$`97.5 %`[7]
uci_df$mi_beta7[i] <-as.data.frame(confint(lm_impute))$`97.5 %`[8]

## brms: first time we fit and save model, afterwards we update to save compile time

if(i == 1){
 bform <- bf(x1 ~ x2 + x3 + y2 + mi(y1)) + 
  bf(x2 ~ x3 + y2 + mi(y1)) + 
  bf(x3 ~ y2 + mi(y1)) + 
  bf(y2 ~  treatment * prettest * mi(y1)) + 
  bf(y1 | mi() ~ 1) +
  set_rescor(FALSE)
  

brm1 <- brm(bform, df_ml_brm, 
            save_model = "main_effect_model.stan",
            silent = TRUE)
}

else{
brm1 <- update(brm1, newdata = df_ml_brm,
            silent = TRUE)
}

sumb1 <- summary(brm1)



point_df$brm_beta0[i] <- summary(brm1)$fixed["y2_Intercept","Estimate"]
point_df$brm_beta1[i] <- summary(brm1)$fixed["y2_treatment","Estimate"]
point_df$brm_beta2[i] <- summary(brm1)$fixed["y2_prettest","Estimate"]
point_df$brm_beta3[i] <- summary(brm1)$fixed["y2_miy1","Estimate"]
point_df$brm_beta4[i] <- summary(brm1)$fixed["y2_treatment:prettest","Estimate"]
point_df$brm_beta5[i] <- summary(brm1)$fixed["y2_miy1:treatment","Estimate"]
point_df$brm_beta6[i] <- summary(brm1)$fixed["y2_miy1:prettest","Estimate"]
point_df$brm_beta7[i] <- summary(brm1)$fixed["y2_miy1:treatment:prettest","Estimate"]
point_df$brm_sigma[i] <- summary(brm1)$spec_pars["sigma_y1", "Estimate"]


lci_df$brm_beta0[i] <- summary(brm1)$fixed["y2_Intercept","l-95% CI"]
lci_df$brm_beta1[i] <- summary(brm1)$fixed["y2_treatment","l-95% CI"]
lci_df$brm_beta2[i] <- summary(brm1)$fixed["y2_prettest","l-95% CI"]
lci_df$brm_beta3[i] <- summary(brm1)$fixed["y2_miy1","l-95% CI"]
lci_df$brm_beta4[i] <- summary(brm1)$fixed["y2_treatment:prettest","l-95% CI"]
lci_df$brm_beta5[i] <- summary(brm1)$fixed["y2_miy1:treatment","l-95% CI"]
lci_df$brm_beta6[i] <- summary(brm1)$fixed["y2_miy1:prettest","l-95% CI"]
lci_df$brm_beta7[i] <- summary(brm1)$fixed["y2_miy1:treatment:prettest","l-95% CI"]
lci_df$brm_sigma[i] <- summary(brm1)$spec_pars["sigma_y1", "l-95% CI"]


uci_df$brm_beta0[i] <- summary(brm1)$fixed["y2_Intercept","u-95% CI"]
uci_df$brm_beta1[i] <- summary(brm1)$fixed["y2_treatment","u-95% CI"]
uci_df$brm_beta2[i] <- summary(brm1)$fixed["y2_prettest","u-95% CI"]
uci_df$brm_beta3[i] <- summary(brm1)$fixed["y2_miy1","u-95% CI"]
uci_df$brm_beta4[i] <- summary(brm1)$fixed["y2_treatment:prettest","u-95% CI"]
uci_df$brm_beta5[i] <- summary(brm1)$fixed["y2_miy1:treatment","u-95% CI"]
uci_df$brm_beta6[i] <- summary(brm1)$fixed["y2_miy1:prettest","u-95% CI"]
uci_df$brm_beta7[i] <- summary(brm1)$fixed["y2_miy1:treatment:prettest","u-95% CI"]
uci_df$brm_sigma[i] <- summary(brm1)$spec_pars["sigma_y1", "u-95% CI"]



print(i)
}

t2 <- Sys.time() # save finish time

t2 - t1

saveRDS(point_df, "simple sim results.RDS")
}
```

Here is each parameter as recovered by each model (where possible)

```{r message = FALSE, warning = FALSE}


point_df_long <- point_df %>% pivot_longer(1:ncol(.), names_to = "variable",
                                           values_to = "estimate")  %>%
  mutate(
    model = str_remove(variable, "_[^_]*$"),
    parameter = str_extract(variable, "[^_]+$")) %>% left_join(par_df) %>%
 mutate(bias = estimate - true_value)


point_df_long$model <- factor(point_df_long$model, levels = c("true","between",
                                                              "full_pretest",
                                                              "fiml","mi","brm"))

point_df_long$definition <- factor(point_df_long$definition, levels = unique(point_df_long$definition))


ggplot(point_df_long, aes(x = model, y = estimate, fill = model, color = model)) +
  geom_hline(aes(yintercept = true_value)) +
  facet_wrap(. ~ definition, nrow = 3, scales = "free") +
  theme_minimal() + geom_violin(alpha = .6) + geom_jitter(alpha = .25) + 
   theme(legend.position = "none",
  axis.text.x = element_text(angle = 45, hjust = 1)
)


```
